---
title: "Analysis Replication"
Author: Audrey Tjahjadi
output: html_document
---

```{r}
f <-"C:/Users/Audrey/Desktop/Nunes_2015(1).csv"
d <- read.csv(f, header = TRUE)
head(d)
```

```{r}
#this dataframe contains only values from the P. palmata species
d1 <- data.frame(d[1:227,])
d1
```
```{r}
#this dataframe contains only values from S. latissima
d2 <- data.frame(d[228:386,])
d2
```

#Analysis 1: Determining the most useful model for NPP
## Assessment of Normality

Net Primary Productivity in this paper was determined as the difference in dissolved oxygen concentrations between measurements taken at the start of the experiment and at the end of the light incubation period.
First, as in the paper, I used a qqnorm plot along with a histogram to show that the data for NPP is clearly not linear or normal.  

```{r}
par(mfrow = c(2,2))
hist(d1$NPP.O2, xlab = "Difference in O2 (NPP)", main = "NPP of P. palmata")
qqnorm(d1$NPP.O2, main = "NPP of P. palmata")
hist(d2$NPP.O2, xlab = "Difference in O2 (NPP)", main = "NPP of S. latissima")
qqnorm(d2$NPP.O2, main = "NPP of S. latissima")
```

##Comparing possible models using AIC and log likelihoods

In the paper, it seemed to me that the indicator of 'OA' was the pH (Potentiometric) measurement and not the pH calculated by seacarb though this was not made clear. Therefore, I used the potentiometric values for my analysis. The 'Treat' column may also have been used for OA as this shows the concentration of CO2 in each sample, but since these values matched up with the pH values, I used the pH values instead. 

###Models for P. palmata NPP

```{r}
#all of the possible models that were considered in the study 
#Duration is Time and Potentiometric.pH is OA as they appear in the paper.

m1 <- lm(data = d1, NPP.O2 ~ Duration * Potentiometric.pH)
m2 <- lm(data = d1, NPP.O2 ~ Duration + Potentiometric.pH)
m3 <- lm(data = d1, NPP.O2 ~ Duration)
m4 <- lm(data = d1, NPP.O2 ~ Potentiometric.pH)
m5 <- lm(data = d1, NPP.O2 ~ 1)
```

This paper used forward selection and added predictor variables to make increasing more complex models to see which model fit best. 

#Analysis 2: Finding the best model for respiration
Respiration values in this paper were taken as the difference in dissolved oxygen between measurements taken at the start of the experiment and the end of the dark incubation period. 

The respiration analysis was done in a similar manner to the NPP analysis. 

```{r}
par(mfrow = c(2,2))
hist(d1$Resp.O2, xlab = "Change in Dissolved O2 (Respiration)", main = "Respiration of P. palmata")
qqnorm(d1$Resp.O2, main = "Net Primary Productivity")
hist(d2$Resp.O2, xlab = "Change in Dissolved O2 (Respiration)", main = "Respiration of S. latissima")
qqnorm(d2$Resp.O2, main = "Net Primary Productivity")
```


